%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{fontawesome}
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\usepackage[latin1]{inputenc}  
\usepackage{eurosym}
\usepackage[T1]{fontenc}
\usepackage[francais]{babel}
\name{Théo Compérot} % Your name
\address{30 av. de la Grande Armée \\ Paris, 75017} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\faMobilePhone\quad(+33)6 47 95 66 27 \quad \\ \quad \faEnvelopeO \quad theo.comperot@gmail.com\quad \\ \quad \faLinkedin \quad théo-compérot} % Your phone number and email
\begin{document} 

%----------------------------------------------------------------------------------------
%	A rajouter:
% 		- Parler de dku
%		- Parler des données L1 / L2.
%		- Passive posting (waiting time analysis, modèles de censure, kaplan-meier)
%		- Parler des participants
%		- Parler des gros sets de données
%		- Parler du nb de données
%----------------------------------------------------------------------------------------

%\centering\small{Engineering student looking for a 6-month internship in statistics and machine learning, starting around June 2019}
\begin{rSection}{Professional summary} 

Highly motivated and detail-oriented quantitative analyst in market microstructure with two years hands-on experience. Strong programming skills in Python and experience in dealing with large datasets. Extensive use of Level 1, 2 and 3 market data from main European Primary exchanges and MTFs. Published two research papers on retail flow execution. Currently writing one on Price Reversion and its main drivers across main European exchanges. 

\end{rSection}

\begin{rSection}{Work Experiences} 

\begin{rSubsection}{Euronext Paris}{\bf March 2020 - Present}{Quant Research Analyst}{Paris}
\item Price reversion across lit venues: analysis of price changes occurring before and after elementary executions on lit markets. Identification of Price Reversion main drivers (volatility, spread, orderbook imbalance). Comparison between participant types (LP, Client, House \& Retail). Publication expected in February 2022. \smallskip
\item Passive posting resting time across lit venues: compared execution and cancellation probability for passive limit orders inserted at EBBO on main European lit exchanges. \smallskip
\item Research in retail flow trading costs and mechanisms. Published research:
\begin{itemize}
    \item \textit{No free lunch as trading on Equiduct's "Apex" turns out to be more costly than on Euronext's "BestofBook"} (October 2020). Compared Euronext retail execution service and with Equiduct's. Showed that Euronext's BestofBook ouperforms Apex, especially during period of price volatility. 
    \item \textit{VBBO Trading: a best execution solution for Retail Investors or for Market Makers?} (July 2020). Studied extensively VBBO trading on Equiduct's Apex service for retail flow. Based on QuantHouse data, compared VBBO prices with EBBO prices, showed a deterioration with trade size and orderbook spread. 
\end{itemize}
\item Development of best execution reports for retail brokers.

\end{rSubsection}

\begin{rSubsection}{BNP Paribas Asset Management}{\bf June 2019 - Sept 2019}{Data Scientist / Quantitative analyst}{Paris}
\item[] Credit project : Portfolio optimization based on various factors from value, quality and momentum. Showed that those factors play an important role in explaining the cross-section of corporate bond expected returns. In-depth study of integer programming.
\end{rSubsection}

\begin{rSubsection}{French Ministry of Education}{\bf Oct 2017 - June 2018}{Oral examiner in Mathematics in Classes Préparatoires aux Grandes Ecoles}{Paris}
\item[]\vspace{-1\baselineskip}
\end{rSubsection}

%\begin{rSubsection}{AstuciX}{\bf Jul 2017 - Sep 2017}{Mathematics courses designer}{Paris}
%\item[] Designed mathematics courses for Classes Préparatoires aux Grandes Ecoles students
%\end{rSubsection}

%\begin{rSubsection}{Reach5}{\bf Jun 2017 - Aug 2017}{Summer intern}{Paris}
%\item Analyzed user preferences, reduced dimension of a sparse dataset based on PCA and SVD algorithms \smallskip
%\item Predicted sociodemographic features based on Lasso regression\smallskip
%\item Identified typical profiles based on various clustering algorithms  \smallskip
%\end{rSubsection}


\end{rSection}



\begin{rSection}{Education}

\begin{rSubsection}{ENS Paris Saclay}{\bf Sep 2018 - Jun 2019}{Master in Applied Mathematics, Vision and Learning}{Cachan}
\item \textbf{Relevant Coursework} Probabilistic Graphical Models, Reinforcement Learning, Convex Optimization, Advanced Learning for Text and Graph Data, Deep Learning, Kernel Methods \smallskip
\end{rSubsection}

\begin{rSubsection}{ENSAE ParisTech - Grande Ecole d'Ingénieur}{\bf Sep 2016 - Jun 2019}{Master in Applied Mathematics and Data Science, Mathematics and Statistics Major}{Paris}
\item \textbf{Relevant Coursework} Computational Statistics, Statistical Learning, High-dimensional Statistics, Non parametric Statistics, Stochastic Processes, Optimization, Time Series Analysis.\smallskip
\item \textbf{Academic Projects} Tested the resistance to outliers of regression trees and built robust versions of it (Python), Created a movie recommendation system based on collaborative filtering and matrix factorization (Python), Predicted monthly payments from sociodemographic features based on regressions for the French Red Cross (Python and R) 
\end{rSubsection}

\begin{rSubsection}{Lycée Charlemagne - Classes Préparatoires aux Grandes Ecoles}{\bf Sep 2013 - Jun 2016}{Mathematics and Physics Major, MPSI-MP*}{Paris}
%\item \textbf{Computer science option} Propositional Calculus, Automata, Graph Theory   \smallskip
%\item \textbf{Academic Projects} Studied the distribution and evolution of a trajectory in mathematical plane convex billiard tables, Implemented various error-correcting codes and in particular cyclic redundancy checks (Python)
\end{rSubsection}

\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------

\begin{rSection}{Programming skills and interests}

\begin{rSubsection}{}{}{}{}
\item \textbf{Programming} Python, R, SAS, SQL, CamlLight \smallskip
\item \textbf{Languages} French (native), English (fluent, TOEIC : 975/990) \smallskip
\item \textbf{Piano} Played piano for 13 years (2nd Prize at the Paris musical contest) \smallskip 
\item \textbf{Handball} Played Handball (12 years) at Paris Saint-Germain  (3rd of French Championship in
2012)

\end{rSubsection}

%------------------------------------------------



\end{rSection}

%----------------------------------------------------------------------------------------


\end{document}
